Multiple deprivation index using small area estimation methods: an application for the adult population in Colombia

### 2022-02-01 Paper_MPI_CEPAL/main.tex
Preguntas a discutir

\subsection{SAE Methods}
In order to performing a complete poverty mapping and obtaining a local picture of
poverty in a region, the use of an adequate estimation method becomes necessary.
Unfortunately national surveys often are not suitable to give reliable statistical information
at local levels to cover all regions within a country due to the high costs.
Small area procedures are estimation procedures for parameters under very small
sample sizes. For sufficiently large sample sizes, traditional estimators, such as the
mean estimators, produce very convincing results, but when applied to small sample
sizes, such estimators often only have very limited reliability. This is often the case
if the subject requires the data to be split into many small categories, e.g. municipalities.
Even large surveys in a country will contain administrative units from
which only very few or even no households have been sampled. For such domains, in
practice, the sampling error is often huge ([Rao03]). Luckily there is an alternative
to the classical estimators, the model based methods, which have been developed
further in recent years. These methods use model assumptions to reduce the sampling
error. The small area estimation methods, in particular, based on generalized
linear mixed models are part of this class of methods. Their basic principle is to
improve the estimation by extending the original too small sample. Explanatory a
survey data set might be extended by the census of the whole state, even though
the variable of interest is missing in the census data. Under strict assumptions on the sample and its distribution, such model based procedures result
in much better estimates than classical procedures.

@@

\begin{itemize}
    \item Parametric bootstrap based on \cite{moretti2021small}
\end{itemize}

\section{Validation: Design-based simulation study}
\begin{itemize}
    \item In this section we illustrate some of the aspects of composite indicators in a SAE context evaluation. In particular, combining the results of model prediction we described
in sections bellow, we present results for the estimation of the MPI. We discuss how the design-based simulation results can guide the production of the
final set of MPI estimates in a SAE context.
Analysis with the original sam. And we ple. %Table 3.2 presents summaries over municipalities of point, root MSE (RMSE) and CV estimatescomputed using the original data supplied to us by CEPAL and estimated MSEs under the assumed models. 
\item Evaluation of the performance of the proposed methodology in the context of a real population and realistic sampling methods.  
    \item Illustrating aspects of SAE evaluation using the GEIH data %ENIGH
\item
\end{itemize}

@@

@@

\begin{table}[ht] 
\small{
	\caption{Summary statistics for sample and population sizes}
	}
	\centering
		\begin{tabular}{lrrrrrr}
		\hline
         &Min &1st Q &Median& Mean & 3rd Q & Max \\ 
		\hline
		  Sample domains &  \multirow{2}{*}{12} & \multirow{2}{*}{62} & \multirow{2}{*}{103}& \multirow{2}{*}{144.37} & \multirow{2}{*}{191} & \multirow{2}{*}{877}   \\
		  (In-sample: \%) & &&&&&\\
		  Population domains &    &  & &  &  & \\
			\hline
	\end{tabular} 
		\label{tab:sizes}
\end{table}

\begin{table}[ht]
\begin{center}
\small{
	\caption{Coefficients of variation of the direct and model-based estimates for income (mean)}
	\centering
		\begin{tabular}{lrr}
		\hline
			CV	& Direct&  EBP\\
				\hline

			%	         \hline
				     	 Min &&\\
						  1st Q. &&\\
				 		 Median  &&\\
						Mean&&\\
				         3rd Q.&&\\
				          Max  &&\\
			\hline
	\end{tabular}
	}
	\end{center}
\end{table}

@@

\begin{itemize}
    \item Similar description? do we need two different sections?
    \item Tables, plots and maps.

\end{itemize}

@@

\begin{itemize}
    \item Genenal incidence of poverty by: sex, age group, area.
    \item Description by indicator /domains
    \item Provide information with coefficients of variation 
\end{itemize}

>>>>

\subsection{SAE Methods}

\textcolor{red}{A definir: }
\begin{itemize}
\item \textcolor{red}{Porqué decidimos usar el EBP de Guadarrama con transformación log-shift? Cómo justificamos que esta es la mejor alternativa? Se podría justificar comparando ``clásico" EBP con EBP de Guadarrama, y/o distintas transformaciones }
\item \textcolor{red}{Lo mismo para el EPP, porqué el Plug-in en lugar del EBP para variables binarias?}
\end{itemize}

In order to performing a complete poverty mapping and obtaining a local picture of
poverty in a region, the use of an adequate estimation method becomes necessary.
Unfortunately national surveys often are not suitable to give reliable statistical information
at local levels to cover all regions within a country due to the high costs.
Small area procedures are estimation procedures for parameters under very small
sample sizes. For sufficiently large sample sizes, traditional estimators, such as the
mean estimators, produce very convincing results, but when applied to small sample
sizes, such estimators often only have very limited reliability. This is often the case
if the subject requires the data to be split into many small categories, e.g. municipalities.
Even large surveys in a country will contain administrative units from
which only very few or even no households have been sampled. For such domains, in
practice, the sampling error is often huge ([Rao03]). Luckily there is an alternative
to the classical estimators, the model based methods, which have been developed
further in recent years. These methods use model assumptions to reduce the sampling
error. The small area estimation methods, in particular, based on generalized
linear mixed models are part of this class of methods. Their basic principle is to
improve the estimation by extending the original too small sample. Explanatory a
survey data set might be extended by the census of the whole state, even though
the variable of interest is missing in the census data. Under strict assumptions on the sample and its distribution, such model based procedures result
in much better estimates than classical procedures.

@@

\textcolor{red} {Decidir qué vamos a hacer con el MSE??}
\begin{itemize}
    \item \textcolor{red} {Bootstrap para obtener cada MSE por separado?, reportamos MSE independientemente?}
    \item \textcolor{red} {Bootstrap para obtener cada MSE conjunto? ``sumamos" simplemente o buscamos otra alternativa? }
\end{itemize}

\section{Validation: Design-based simulation study}

\textcolor{red} {Queremos validar el MSE?}
\

\begin{itemize}
    \item In this section we illustrate some of the aspects of composite indicators in a SAE context evaluation. In particular, combining the results of model prediction we described
in sections bellow, we present results for the estimation of the MPI. We discuss how the design-based simulation results can guide the production of the
final set of MPI estimates in a SAE context.
Analysis with the original sam. And we ple. %Table 3.2 presents summaries over municipalities of point, root MSE (RMSE) and CV estimatescomputed using the original data supplied to us by CEPAL and estimated MSEs under the assumed models. 
\item Evaluation of the performance of the proposed methodology in the context of a real population and realistic sampling methods.  
    \item Illustrating aspects of SAE evaluation using the GEIH data %ENIGH
\item
\end{itemize}

@@

\textcolor{red}{Iniciar con descripción del modelo. No hay seleccion de variables, ambos modelos usan las mismas. Por esto podríamos decidir si al iniciar la sección de resultados, queremos presentar las variables utilizadas, los tamaños de muestra, población, dominios en /fuera de muestra, etc.?}

@@

\

\begin{table}[ht] 
\small{
	\caption{Summary statistics for sample and population sizes}
	}
	\centering
		\begin{tabular}{lrrrrrr}
		\hline
         &Min &1st Q &Median& Mean & 3rd Q & Max \\ 
		\hline
		  Sample domains &  \multirow{2}{*}{} & \multirow{2}{*}{} & \multirow{2}{*}{}& \multirow{2}{*}{} & \multirow{2}{*}{} & \multirow{2}{*}{}   \\
		  (In-sample: \%) & &&&&&\\
		  Population domains &    &  & &  &  & \\
			\hline
	\end{tabular} 
		\label{tab:sizes}
\end{table}

\begin{itemize}
\item \textcolor{red}{Chequear diagnósticos de los residuos}
\item  \textcolor{red}{QQ plots}
\item  \textcolor{red}{Indicadores básicos: R2, ICC}
\item \textcolor{red}{Comparamos estos resultados con distintas transformaciones o no?}
\end{itemize}

@@

\begin{itemize}
    \item  \textcolor{red}{Decidir si describimos las variables del modelo otra vez aquí o una subsección inicial, al comienzo de la sección de resultados}
    \item  \textcolor{red}{Chequear residuos para los efectos aleatorios: QQplot y Shapiro test}
    \item \textcolor{red}{análisis de clasificación con los datos de encuesta: sensibilidad, especificidad, exactitud}
\end{itemize}
\end{itemize}

@@

\begin{itemize}
    \item General incidence of poverty by: sex, age group, area.
    \item Description by indicator /domains
    \item Provide information with coefficients of variation 
\end{itemize}
